### 2020-08-15 ChapterBackground/chapterBackground.tex
Updated: SpatialOS subsection

HLA is very similar to the model used by SpatialOS \cite{SpatialOS}, which also uses a runtime, however, the implementation details of SpatialOS's runtime are not public knowledge.

HLA is ideal for heterogeneous distributed simulations and for re-use with different types of simulations. However, there are some disadvantges to this architecture:
\begin{enumerate}
	\item It increases latency between simulations as communication must go through the run time \item It does not allow for any optimisations to be performed in the run time as the run time is not aware of the semantics of the simulations.
\end{enumerate}

In the case of real-time physics, we can assume the use of either homogeneous simulations or at least simulations that will be simulating physics with a large degree of shared semantics between simulations (as all simulations are dealing with physical simulation). As a result of this, there is little to no advantage gained in using the HLA architecture and direct communication between servers has the benefit of lower latency between servers.

>>>>

HLA is ideal for heterogeneous distributed simulations and for re-use with different types of simulations. However, there are some disadvantages to this architecture:
\begin{enumerate}
	\item It increases latency between simulations as communication must go through the run time \item It does not allow for any optimisations to be performed in the run time as the run time is not aware of the semantics of the simulations.
\end{enumerate}

\subsection{SpatialOS}
SpatialOS uses a very similar architecture to HLA which also uses a runtime and 'workers' which are equivalent to federates \cite{SpatialOS}. A key difference between HLA and SpatialOS is that in SpatialOS the full entity data of all entities is stored within the run-time (as opposed to just attribute metadata and associations in HLA) and each worker stores a copy of a subset of the entities, which it is responsible for \cite{Introduc36:online}. Each worker communicates updates for the entities it is responsible for, which then get disseminated by the runtime to other workers with registered interest in those entities.

\subsection{Distributed Virtual Environments - Summary}
In the case of real-time physics, we can assume the use of either homogeneous simulations or at least simulations that will be simulating physics with a large degree of shared semantics between simulations (as all simulations are dealing with physical simulation). As a result of this, there is little to no advantage gained in using the HLA architecture or similar and direct communication between servers has the benefit of lower latency between servers.
